\LARGE \bf Grupo Bimbo Inventory Demand Data Science Report

### 2024-07-16 src/data-science-project/data_science_project/docs/paper/paper.tex
Paper Features
Paper Evaluation 1.0

        \item Data Transformation:
        \begin{itemize}
                \item Normalization and Scaling: Numerical features were normalized and scaled to ensure all features contribute equally to the model. StandardScaler from sklearn was used to transform features to have zero mean and unit variance.
                \item Encoding Categorical Variables: Categorical variables were converted into numerical values using one-hot encoding for nominal variables and label encoding for ordinal variables.
        \end{itemize}

        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
        \begin{itemize}
                \item Temporal Features: New temporal features such as the day of the week, month, and lag features for past sales data were created to capture temporal dependencies and seasonality in the data.
                \item Interaction Features: Interaction features between different variables were created to capture complex relationships within the data.
                \item External Economic Indicators: The bi-weekly inflation rate and consumer confidence index were merged with the primary dataset to capture the economic conditions impacting product demand.
        \end{itemize}
\end{itemize}

>>>>

        \item Data Transformation:
        \begin{itemize}
                \item Normalization and Scaling: Numerical features were normalized and scaled to ensure all features contribute equally to the model. StandardScaler from sklearn was used to transform features to have zero mean and unit variance.
        \end{itemize}

        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
        \begin{itemize}
                \item Temporal Features: Change to week features to datetime format and put as index.
                \item Interaction Features: Interaction features between different variables were created to capture complex relationships within the data.
                \begin{itemize}
                        \item \textbf{Sales\_Growth\_Rate\_1}: Demand for the same product in the previous week.
                        \item \textbf{Sales\_Growth\_Rate\_2}: Demand for the same product two weeks ago.   
                \end{itemize}
                \item External Economic Indicators: The bi-weekly inflation rate and consumer confidence index were merged with the primary dataset to capture the economic conditions impacting product demand.
        \end{itemize}
\end{itemize}
